Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-02-25 analysis/paper/paper.Rmd
x-axis tick labels for PCA contribution plots

```{r contribution_plots}
# let's look at all the PCs and how much each original # variable contributes to them

@@

# TODO: decode the x-axis labels on the scree plot so we can describe in
# terms of actual flake dimension, write some sentences to describe and interpret

@@

# This is a temporary fix just to get the labels looking nice for now; there is most certainly a cleaner way to do this
# My fix did not work. I will have to create a temp table showing the values for now

# PC1_contrib[["plot_env"]][["xx"]] <- as.factor(c("X Value: Top Left",
#                                              "Y Value: Top Left",
#                                               "Y Value: Mid-Upper Left",
#                                               "X Value: Mid-Lower Left",
#                                               "Y Value: Mid-Lower Left",
#                                               "X Value: Bottom Left",
#                                               "Y Value: Bottom Left",
#                                               "X Value: Distal Tip",
#                                               "Y Value: Distal Tip",
#                                               "X Value: Bottom Right",
#                                               "Y Value: Bottom Right",
#                                               "X Value: Mid-Lower Right",
#                                               "Y Value: Mid-Lower Right",
#                                               "X Value: Mid-Upper Right",
#                                               "Y Value: Mid-Upper Right",
#                                               "X Value: Top Right",
#                                               "Y Value: Top Right"))
#

#iris$Species[iris$Species == 'virginica'] <- 'setosa'

#PC1_contrib[["plot_env"]][["data"]][["name"]][PC1_contrib[["plot_env"]][["data"]][["name"]] == '5.X'] <- "X Value: Distal Tip"

#PC1_contrib[["plot_env"]][["data_sum"]][["name"]] <- as.factor(c(1:18))

output_meanings <-tibble(data.frame(c("X Value: Top Left",
         "Y Value: Top Left",
         "X Value: Mid-Upper Left",
         "Y Value: Mid-Upper Left",
         "X Value: Mid-Lower Left",
         "Y Value: Mid-Lower Left",
         "X Value: Bottom Left",
         "Y Value: Bottom Left",
         "X Value: Distal Tip",
         "Y Value: Distal Tip",
         "X Value: Bottom Right",
         "Y Value: Bottom Right",
         "X Value: Mid-Lower Right",
         "Y Value: Mid-Lower Right",
         "X Value: Mid-Upper Right",
         "Y Value: Mid-Upper Right",
         "X Value: Top Right",
         "Y Value: Top Right"),
       c("1X",
         "1Y",
         "2X",
         "2Y",
         "3X",
         "3Y",
         "4X",
         "4Y",
         "5X",
         "5Y",
         "6X",
         "6Y",
         "7X",
         "7Y",
         "8X",
         "8Y",
         "9X",
         "9Y")))

output_meanings <- setNames(output_meanings, c("Landmark Value", "Computer Output"))

plot_grid(PC1_contrib, 
          PC2_contrib)
 output_meanings

@@

  <!-- Could not figure out how to change the labels on the x axis for the two bar charts, so I included a small table with the human-meaningful values for now. This must be fixed later-->

  Figure \@ref(fig:contribution_plots) shows the relative contribution of each of the original 18 variables put through our PCA. Looking at the supplementary table, we can see that the first principal component is primarily composed of the x-value for the distal tip landmark, with smaller contributions from the y-values from the two upper-most and mid-upper points. The second primary dimension is composed largely of the y-values for bottom-most and upper-most points.

>>>>

```{r contribution-plots, fig.cap="Plots showing the contribution of landmarks to the overall shape variation among flakes."}
# let's look at all the PCs and how much each original # variable contributes to them

@@

@@

plot_grid(

PC1_contrib +
  scale_x_discrete(labels = 
  as.factor(c("X Value: Top Left",
              "Y Value: Top Left",
              "Y Value: Mid-Upper Left",
              "X Value: Mid-Lower Left",
              "Y Value: Mid-Lower Left",
              "X Value: Bottom Left",
              "Y Value: Bottom Left",
              "X Value: Distal Tip",
              "Y Value: Distal Tip",
              "X Value: Bottom Right",
              "Y Value: Bottom Right",
              "X Value: Mid-Lower Right",
              "Y Value: Mid-Lower Right",
              "X Value: Mid-Upper Right",
              "Y Value: Mid-Upper Right",
              "X Value: Top Right",
              "Y Value: Top Right",
              "xx"))),
          PC2_contrib + 
    scale_x_discrete(labels = 
  as.factor(c("X Value: Top Left",
              "Y Value: Top Left",
              "Y Value: Mid-Upper Left",
              "X Value: Mid-Lower Left",
              "Y Value: Mid-Lower Left",
              "X Value: Bottom Left",
              "Y Value: Bottom Left",
              "X Value: Distal Tip",
              "Y Value: Distal Tip",
              "X Value: Bottom Right",
              "Y Value: Bottom Right",
              "X Value: Mid-Lower Right",
              "Y Value: Mid-Lower Right",
              "X Value: Mid-Upper Right",
              "Y Value: Mid-Upper Right",
              "X Value: Top Right",
              "Y Value: Top Right",
              "xx")))
  )

@@

Figure \@ref(fig:contribution-plots) shows the relative contribution of each of the original 18 variables put through our PCA. Looking at the supplementary table, we can see that the first principal component is primarily composed of the x-value for the distal tip landmark, with smaller contributions from the y-values from the two upper-most and mid-upper points. The second primary dimension is composed largely of the y-values for bottom-most and upper-most points.
